### 2024-04-06 thesis/appendix.tex
March 31st 2024
April 6th 2024

\chapter{Appendix}
\section{Feature Map Normalization}\label{appendix:new_feature}
\begin{proof}
\begin{align*}
    \|
    \phi^{new}(x)\|_{\mathcal{H}}^{2} &= \|\frac{\phi(x)}{\|\phi(x)\|_{\mathcal{H}}}
    \|_{\mathcal{H}}^{2}
    \\
    &=
    \|
    \frac{\phi(x)}
    {\sqrt{k(x,x)}}
    \|_{\mathcal{H}}^{2}
    \\
    &=
    \langle
    \frac{\phi(x)}
    {\sqrt{k(x,x)}}
    ,
    \frac{\phi(x)}
    {\sqrt{k(x,x)}}
    \rangle_{\mathcal{H}}
    \\
    &=
    \frac{1}{\sqrt{k(x,x)^{2}}}
    \langle
    \phi(x)
    ,
    \phi(x)
    \rangle_{\mathcal{H}}
    \\
    &=1
\end{align*}
\end{proof}

\section{Cross validation}\label{appendix:cross_validation}

\section{Quantile regressor extensive comparison}\label{appendix:quantile_regressor_extensive_comparison}
\subsection{Boston housing dataset}
The Boston housing dataset \href{https://www.kaggle.com/datasets/altavish/boston-housing-dataset}{https://www.kaggle.com/datasets/altavish/boston-housing-dataset} contains information about various attributes for suburbs in Boston.
There are 13 indipendent variables:
\begin{itemize}
\item CRIM per capita crime rate by town
\item ZN proportion of residential land zoned for lots over 25,000 sq.ft.
\item INDUS proportion of non-retail business acres per town.
\item CHAS Charles River dummy variable (1 if tract bounds river; 0 otherwise)
\item NOX nitric oxides concentration (parts per 10 million)
\item RM average number of rooms per dwelling
\item AGE proportion of owner-occupied units built prior to 1940
\item DIS weighted distances to five Boston employment centres
\item RAD index of accessibility to radial highways
\item TAX full-value property-tax rate per 10,000
\item PTRATIO pupil-teacher ratio by town
\item B $1000(Bk - 0.63)^2$ where Bk is the proportion of afroamericans by town
\item LSTAT lower status of the population
\end{itemize}
The dependent variable is MEDV, that is the median value of owner occupied homes in \$1000's

@@

\section{Cross validation}
Cross validation directly estimates the expected test error
\begin{equation}
    Err=\mathbb{E}\left[L\left(Y,\hat{f}(X)\right)\right]=\mathbb{E}\left[Err_{\Tau}\right]
\end{equation}
$Err_{\Tau}$ is the prediction error over an independent test sample
\begin{equation}
    \mathbb{E}_{\Tau}=\mathbb{E}\left[L\left(Y,\hat{f}(X)\right)| \Tau \right]
\end{equation}
That is $Err$ is the average over everything that is random: X,Y and the training set $\Tau$ used to learn $\hat{f}$. Hence, our interest lies in estimating the $Err$ quantity in order to guide model selection.
\subsection{K-fold cross validation}
K-fold cross validation splits the data into K roughly equally sized parts, then K models are trained. For k from 1 to K we train the kth model on the whole dataset except the kth partition. Next,  the prediction error of the kth fitted model is computed. Finally averaging all the k prediction erros we obtain an estimate for the expected test error. We select the model which performs best in terms of expected prediction error.
\\
Usually, K is set equal to 5 or 10. Leave-one-out cross validation is the case when K is set equal to the size of the data.
% REMEMBER: Parameters allow the model to learn the rules from the data while hyperparameters control how the model is training. Parameters learn their own values from data. In contrast, hyperparameters do not learn their values from data. We need to manually specify them before training the model
\subsection{Gridsearch}
Model performance depends higly on the choice of hyperparameters. Notice, there is no way to get to know them in advance, therefore, all we can do is trying a lot of combinations until we fit a good enough set of hyperparameters. Essentially, gridsearch carries out hyperparameter tuning by performing a search over a predefined hyperparemeters grid. During its search, it tries all possible combination and evaluates the different models %(different hyperparameters define different models)
using cross validation. For example, suppose that the grid contains 100 possible candidates and that we are doing 5-fold cross-validation, then the gridsearch algorithm will carry out 500 iterations.
Therefore, we get an estimate of prediction error for each considered model and this guides us in hyperparameters (model) selection.

@@

\subsection{Data normalization}
With data normalization we transform the range of the feautures to a standard scale.
Such preprocessing step is essential when employing distance based algorithms like svm or k-nearest neighbors. The rationale behind it is that by normalizing data we give an uniform weight to each feature in the learning process; in this way we do not favour larger scale features.
Examples of the most popular features scaling are:
\begin{itemize}
    \item Standard scaler= it computes the standard score z of a sample x
    \\
    z=$\frac{x-\mu}{\sigma}$.
    \item MinMax scaler= it maps every data sample to the range 0, 1.
    \\
    $\frac{x-\min(X)}{\max(X)-\min(X)}$
    \item Robust scaler= it scales features using statistics that are robust to outliers.
    Essentially, it subtracts the median and then scales the data according to the interquantile range.
\end{itemize}
Many other data scaling algorithms exists, we refer the reader to a thorough comparison \cite{scikitscalers}.
\\
We conclude this subsection with a custom example that motivates the need of feature scaling \cite{scikitscale_example}. The idea is to compare the results of modelling the data with k nearest neighbors on the unscaled data against the scaled data. The considered data is the wine recognition dataset \href{https://archive.ics.uci.edu/dataset/109/wine}{https://archive.ics.uci.edu/dataset/109/wine}. The goal for this dataset is recognising from whose cultivator the wine comes based on two features with a completely different scale. The first feature has values in the [0,1000] range while the second feature has values contained in [1,10].
The unscaled and scaled version are compared in figure \ref{fig:feature_scaler_example}
\begin{figure}[!h]
    \includegraphics[width=\textwidth]{images/feature_scaler_example.png}
    \caption{importance of feature scaling}
    \label{fig:feature_scaler_example}
\end{figure}
What we can conclude from the image is that, the model trained on scaled data is greatly better than the other.
On the left, we can see that distances between categories are impacted solely by the larger scale feature. Conversely, on the right, we have that the two features contributing equally in determining the neighbors.

>>>>

\chapter{Appendix}
\section{Feature Map Normalization}\label{appendix:new_feature}
\begin{proof}
\begin{align*}
    \|
    \phi^{new}(x)\|_{\mathcal{H}}^{2} &= \left\|\frac{\phi(x)}{\|\phi(x)\|_{\mathcal{H}}}
    \right\|_{\mathcal{H}}^{2}
    \\
    &=
    \left\|
    \frac{\phi(x)}
    {\sqrt{k(x,x)}}
    \right\|_{\mathcal{H}}^{2}
    \\
    &=
    \langle
    \frac{\phi(x)}
    {\sqrt{k(x,x)}}
    ,
    \frac{\phi(x)}
    {\sqrt{k(x,x)}}
    \rangle_{\mathcal{H}}
    \\
    &=
    \frac{1}{\sqrt{k(x,x)^{2}}}
    \langle
    \phi(x)
    ,
    \phi(x)
    \rangle_{\mathcal{H}}
    \\
    &=1
\end{align*}
\end{proof}

\section{Quantile regressor extensive comparison}\label{appendix:quantile_regressor_extensive_comparison}
This section contains extensive comparison between our kernel quantile regression and other state of the art quantile regressors. We benchmark it on popular machine learning datasets.
\subsection{Boston housing dataset}
The Boston housing dataset \href{https://www.kaggle.com/datasets/altavish/boston-housing-dataset}{https://www.kaggle.com/datasets/altavish/boston-housing-dataset} contains information about various attributes for suburbs in Boston.
There are 13 indipendent variables:
\begin{itemize}
\item CRIM per capita crime rate by town
\item ZN proportion of residential land zoned for lots over 25,000 sq.ft.
\item INDUS proportion of non-retail business acres per town.
\item CHAS Charles River dummy variable (1 if tract bounds river; 0 otherwise)
\item NOX nitric oxides concentration (parts per 10 million)
\item RM average number of rooms per dwelling
\item AGE proportion of owner-occupied units built prior to 1940
\item DIS weighted distances to five Boston employment centres
\item RAD index of accessibility to radial highways
\item TAX full-value property-tax rate per 10,000
\item PTRATIO pupil-teacher ratio by town
\item B $1000(Bk - 0.63)^2$ where Bk is the proportion of afroamericans by town
\item LSTAT lower status of the population
\end{itemize}
The dependent variable is MEDV, that is the median value of owner occupied homes in \$1000's

@@

\section{Cross validation}\label{appendix:cross_validation}
Cross validation directly estimates the expected test error
\begin{equation}
    Err=\mathbb{E}\left[L\left(Y,\hat{f}(X)\right)\right]=\mathbb{E}\left[Err_{\Tau}\right]
\end{equation}
$Err_{\Tau}$ is the prediction error over an independent test sample
\begin{equation}
    \mathbb{E}_{\Tau}=\mathbb{E}\left[L\left(Y,\hat{f}(X)\right)| \Tau \right]
\end{equation}
That is $Err$ is the average over everything that is random: X,Y and the training set $\Tau$ used to learn $\hat{f}$. Hence, our interest lies in estimating the $Err$ quantity in order to guide model selection.
\subsection{K-fold cross validation}
K-fold cross validation splits the data into K roughly equally sized parts, then K models are trained. For k from 1 to K we train the kth model on the whole dataset except the kth partition. Next,  the prediction error of the kth fitted model is computed. Finally averaging all the k prediction erros we obtain an estimate for the expected test error. We select the model which performs best in terms of expected prediction error.
\\
Usually, K is set equal to 5 or 10. Leave-one-out cross validation is the case when K is set equal to the size of the data.
% REMEMBER: Parameters allow the model to learn the rules from the data while hyperparameters control how the model is training. Parameters learn their own values from data. In contrast, hyperparameters do not learn their values from data. We need to manually specify them before training the model
\subsection{Gridsearch}
Model performance depends higly on the choice of hyperparameters. Notice, there is no way to get to know them in advance, therefore, all we can do is trying a lot of combinations until we fit a good enough set of hyperparameters. Essentially, gridsearch carries out hyperparameter tuning by performing a search over a predefined hyperparemeters grid. During its search, it tries all possible combination and evaluates the different models %(different hyperparameters define different models)
using cross validation. For example, suppose that the grid contains 100 possible candidates and that we are doing 5-fold cross-validation, then the gridsearch algorithm will carry out 500 iterations.
Therefore, we get an estimate of prediction error for each considered model and this guides us in hyperparameters (model) selection.

@@

\subsection{Data normalization}\label{appendix:normalization}
With data normalization we transform the range of the feautures to a standard scale.
Such preprocessing step is essential when employing distance based algorithms like svm or k-nearest neighbors. The rationale behind it is that by normalizing data we give an uniform weight to each feature in the learning process; in this way we do not favour larger scale features.
Examples of the most popular features scaling are:
\begin{itemize}
    \item Standard scaler= it computes the standard score z of a sample x
    \\
    z=$\frac{x-\mu}{\sigma}$.
    \item MinMax scaler= it maps every data sample to the range 0, 1.
    \\
    $\frac{x-\min(X)}{\max(X)-\min(X)}$
    \item Robust scaler= it scales features using statistics that are robust to outliers.
    Essentially, it subtracts the median and then scales the data according to the interquantile range.
\end{itemize}
Many other data scaling algorithms exists, we refer the reader to a thorough comparison \cite{scikitscalers}.
\\
We conclude this subsection with a custom example that motivates the need of feature scaling \cite{scikitscale_example}. The idea is to compare the results of modelling the data with k nearest neighbors on the unscaled data against the scaled data. The considered data is the wine recognition dataset \href{https://archive.ics.uci.edu/dataset/109/wine}{https://archive.ics.uci.edu/dataset/109/wine}. The goal for this dataset is recognising from whose cultivator the wine comes based on two features with a completely different scale. The first feature has values in the [0,1000] range while the second feature has values contained in [1,10].
The unscaled and scaled version are compared in figure \ref{fig:feature_scaler_example}
\begin{figure}[!h]
    \includegraphics[width=\textwidth]{images/feature_scaler_example.png}
    \caption{importance of feature scaling}
    \label{fig:feature_scaler_example}
\end{figure}
What we can conclude from the image is that, the model trained on scaled data is greatly better than the other.
On the left, we can see that distances between categories are impacted solely by the larger scale feature. Conversely, on the right, we have that the two features contributing equally in determining the neighbors.

### 2024-04-06 thesis/input_files/energymarket.tex
April 6th 2024

\section{Electricity markets}
Electricity markets have gone rapid changes all over the world during the last three decades.
Before this revolution, the power sector was a natural monopoly. In particular, it was characterized by a high vertical integration and by very little market competition. Better technologies in both transmission, generation and distribution are the reasons for such liberal shift. The rationale is simple, a competitive market promotes efficiency and stimulates technical innovation more than a monopoly does.
\\
During the nineties various wholesale electricity markets were established; for example in Chile, Great Britain, the scandinivian block, Australia, New Zealand, the US and Canada. Consequently, new participants each with a specific taks act entered the power market scenario.
\begin{itemize}
    \item Electricity generators produce electricity to be consumed.
    \item Electricity transmission owners 
    move high voltage electricity to electric utility companies whilst ensuring safe and reliable supply.
    \item Electricity grid operators are responsible for scheduling electricity over the transmission network in order to ensure supply demand balance.
    \item Electric utilities deliver power over local lines to consumers. 
    \item Retail energy suppliers purchase electricity in the wholesale market from electricity generators and resell it to consumers.
\end{itemize}

@@

\subsection{Nodal and Zonal Pricing}
Grid configuration and physical limits on electricity lines may lead to congestion. Local marginal price (LMP) and zonal market clearing pricing (ZMCP) are two types of pricing schemes utilized to handle it. The former is adopted in EU contries while the latter is used in the US, figure \ref{fig:eu_zonal} and figure \ref{fig:us_local}.
With ZMCP, prices may differ between zones but are the same within the same area.
LMP is made up by summing the transmission congestion cost, generation marginal cost and the cost of marginal losses at different buses; buses is where a electicity line or several lines are connected.
\begin{figure}[!h]
    \includegraphics[width=\textwidth]{images/eu_zonal.png}
    \caption{Zonal pricing EU \cite{eu_zonal}}
    \label{fig:eu_zonal}
\end{figure}

@@

\section{Renewables}
% https://www.pnnl.gov/explainer-articles/renewable-integration
A pressing challenge facing policymakers today is the energy transition towards cleaner energy, see figure \ref{fig:electricity_production_by_source} for a breakdown on energy production by source. Such move is intended to mitigate the effects of climate change and reduce pollution at the same time.
This transition passes through renewables integration into the electric grid. 
Nevertheless, integrating renewables into the existing electric grid involves several technical challenges. First, we need to develop infrastructures and technologies capable of connecting renewable power plants with the existing grid. For example, connecting renewables power plants located in remote and offshore locations to high voltage powerlines is not trivial.
Additionally, renewables such as wind and solar are characterized by seasonalities and depend heavily on weather conditions. Therefore, balancing the electricity network and mantaining stability will become harder for grid operators; they will need more flexibility in the grid and develop new approaches in order to achieve their goals.

>>>>

\section{Electricity markets}
Electricity markets have gone rapid changes all over the world during the last three decades.
Before this revolution, the power sector was a natural monopoly. In particular, it was characterized by a high vertical integration and by very little market competition. Better technologies in both transmission, generation and distribution are the reasons for such liberal shift. The rationale is simple, a competitive market promotes efficiency and stimulates technical innovation more than a monopoly does.
\\
During the nineties various wholesale electricity markets were established; for example in Chile, Great Britain, the scandinivian block, Australia, New Zealand, the US and Canada. Consequently, new participants, each with a specific task, entered the power market scenario.
\begin{itemize}
    \item Electricity generators produce electricity to be consumed.
    \item Electricity transmission owners 
    move high voltage electricity to electric utility companies whilst ensuring safe and reliable supply.
    \item Electricity grid operators are responsible for scheduling electricity over the transmission network in order to ensure supply demand balance.
    \item Electric utilities deliver power over local lines to consumers. 
    \item Retail energy suppliers purchase electricity in the wholesale market from electricity generators and resell it to consumers.
\end{itemize}
Notice, these functions are not mutually exclusive; that is an entity can provide one or more of these services.

@@

\subsection{Nodal and Zonal Pricing}
Grid configuration and physical limits on electricity lines may lead to congestion. Local marginal price (LMP) and zonal market clearing pricing (ZMCP) are two types of pricing schemes utilized to handle it. The former is adopted in EU contries while the latter is used in the US, figure \ref{fig:eu_zonal} and figure \ref{fig:us_local}.
With ZMCP, prices may differ between zones but are the same within the same area.
On the other hand, LMP is made up by summing the transmission congestion cost, generation marginal cost and the cost of marginal losses at different buses; buses is where a electicity line or several lines are connected.
\begin{figure}[!h]
    \includegraphics[width=\textwidth]{images/eu_zonal.png}
    \caption{Zonal pricing EU \cite{eu_zonal}}
    \label{fig:eu_zonal}
\end{figure}

@@

\section{Renewables}
% https://www.pnnl.gov/explainer-articles/renewable-integration
A pressing challenge facing policymakers today is the energy transition towards cleaner energy, see figure \ref{fig:electricity_production_by_source} for an up to date breakdown on energy production by source. Such move is intended to mitigate the effects of climate change and reduce pollution at the same time.
This transition passes through renewables integration into the electric grid. 
Nevertheless, integrating renewables into the existing electric grid involves several technical challenges. First, we need to develop infrastructures and technologies capable of connecting renewable power plants with the existing grid. For example, connecting renewables power plants located in remote and offshore locations to high voltage powerlines is not trivial.
Additionally, renewables such as wind and solar are characterized by seasonalities and depend heavily on weather conditions. Therefore, balancing the electricity network and mantaining stability will become harder for grid operators; they will need more flexibility in the grid and develop new approaches in order to achieve their goals.

### 2024-04-06 thesis/input_files/implementation.tex
March 23rd 2024
April 6th 2024

- As I explain code scripts go over the test, to 
explain better my ideas.
\section{Linear quantile regression}
The implementation of statsmodels.regression.quantile\_regression.QuantReg has been used.
The model is fitted through iterative reweighted least squares.
\section{Quantile gradient boosting machine}
The implementation of sklearn.ensemble.GradientBoostingRegressor as been used.
\section{Quantile forest}
The implementation of quantile\_forest.RandomForestQuantileRegressor as been used. This estimator is compatible with scikit-learn.
\section{Kernel quantile regression}
Kernel quantile regression had no previously implemented open source library, thus the need of implementing our own version.
\\
The scikit-learn team provides a project template for the creation of estimators compatible with scikit-learn functionalities. Therefore, the KQR class is derived from the scikit-learn BaseEstimator and the mixin class RegressorMixin.
Our KQR class is initialized by providing a quantile, the regularization term C and the rbf kernel bandwidth gamma; the latter are the two hyperparameters of our custom estimator.
\\
In the fit method, we set up and solve the convex optimisation problem by using the cvxopt library. 
When using this library, it is important to keep two things in mind. First this library assumes the quadratic term of the optimisation problem to be multiplied by the 0.5 factor, thus we just have to provide the Q matrix with no 0.5 in front.
Secondly, in order to specify multiple inequalities we have to stack them an provide as a unique matrix.
\\
Once a solution to the convex problem has been found, we create a mask for the support vectors of the estimator in order to estimate the constant term of our kernel quantile regressor.
\\
In the predict method, we pass a matrix X\_eval of independent variables, next we compute the kernel matrix between X\_train and X\_eval and obtain y\_eval with the formula $y=\alpha^\intercal K+b$.
\\
This estimator is compatible with useful scikit-learn in built methods like gridsearch, crossvalidation and scoring rules.
\\
Up to now, there are only two open source implementation of the quantile kernel regression. Nevertheless they are both in R, that is there exists no python, matlab or julia open source implementation. Following are reported the results of a comparative study between our own implementation and the one of the R library kernlab(i guess it is in C or C++ and then binded to R).

>>>>

- As I explain code scripts go over the test, to 
explain better my ideas.
\section{Linear quantile regression}
The implementation of statsmodels.regression.quantile\_regression.QuantReg has been used.
The model is fitted through iterative reweighted least squares.
\section{Quantile gradient boosting machine}
The implementation of sklearn.ensemble.GradientBoostingRegressor has been used.
\section{Quantile forest}
The implementation of quantile\_forest.RandomForestQuantileRegressor has been used. This estimator is compatible with scikit-learn.
\section{Kernel quantile regression}
Kernel quantile regression had no previously implemented open source library, thus the need of implementing our own version.
\\
The scikit-learn team provides a project template for the creation of estimators compatible with scikit-learn functionalities. Therefore, the KQR class is derived from the scikit-learn BaseEstimator and the mixin class RegressorMixin.
Our KQR class is initialized by providing a quantile, the regularization term C and the rbf kernel bandwidth gamma; the latter are the two hyperparameters of our custom estimator.
\\
In the fit method, we set up and solve the convex optimisation problem by using the cvxopt library. 
When using this library, it is important to keep two things in mind. First this library assumes the quadratic term of the optimisation problem to be multiplied by the 0.5 factor, thus we just have to provide the Q matrix with no 0.5 in front.
Secondly, in order to specify multiple inequalities we have to stack them an provide as a unique matrix.
\\
Once a solution to the convex problem has been found, we create a mask for the support vectors of the estimator in order to estimate the constant term of our kernel quantile regressor.
\\
In the predict method, we pass a matrix X\_eval of independent variables, next we compute the kernel matrix between X\_train and X\_eval and obtain y\_eval with the formula $y=\alpha^\intercal K+b$.
\\
This estimator is compatible with useful scikit-learn in built methods like gridsearch, crossvalidation and scoring rules.
\\
Up to now, there are only two open source implementation of the quantile kernel regression. Nevertheless they are both in R, that is there exists no python, matlab or julia open source implementation. Following are reported the results of a comparative study between our own implementation and the one of the R library kernlab
% (i guess it is in C or C++ and then binded to R).
\subsection{Python vs R implementation}
In this section, a comparison study has been carried out in order to inspect the competitiveness of our implementation with the existing one for the R programming language.

### 2024-04-06 thesis/input_files/paper1.tex
April 6th 2024

\section{\href{https://arxiv.org/abs/1605.09522}{Kernel Mean Embedding of Distributions: A Review and Beyond}}
From this first paper \cite{Muandet_2017}, the notation and terms used in the theory of Reproducing Kernel Hilbert Spaces are summarized.
\\
Many algorithms use the inner product as similarity measure between data instances $x, x' \in \mathcal{X}$. However, this inner product spans only the class of linear similarity measures. 
\\
The idea behind kernel methods is to apply a non-linear transformation $\phi$ to the data $x$ 
in order to get a more powerful non linear similarity measure.
\begin{align*}
\phi(x):\mathcal{X} &\longrightarrow \mathcal{F}
    \\
    x&\mapsto \phi(x)
\end{align*}

>>>>

\section{Kernel Mean Embedding of Distributions: A Review and Beyond}
% \href{https://arxiv.org/abs/1605.09522}{
From this first paper \cite{Muandet_2017}, the notation and terms used in the theory of Reproducing Kernel Hilbert Spaces are summarized.
\\
Many algorithms use the inner product as similarity measure between data instances $x, x' \in \mathcal{X}$. However, this inner product spans only the class of linear similarity measures. 
\\
The idea behind kernel methods is to apply a non-linear transformation $\phi$ to the data $x$ 
in order to get a more powerful non linear similarity measure.
\begin{align*}
\phi(x):\mathcal{X} &\longrightarrow \mathcal{F}
    \\
    x&\mapsto \phi(x)
\end{align*}

### 2024-04-06 thesis/input_files/paper2.tex
April 6th 2024

\section{\href{http://proceedings.mlr.press/v33/kanagawa14.pdf}{Recovering Distributions from Gaussian RKHS Embeddings}}
This paper covers the RKHS embedding approach to nonparametric statistical inference \cite{pmlr}.
The idea here is computing an estimate of the kernel mean in order to obtain an approximation of the underlying distribution of the observed random variable.
The kernel mean embedding $\mu_{\mathbb{P}}$ of a probability $\mathbb{P}$ corresponds to the feauture map $\phi(x)$ integrated with respect to the $\mathbb{P}$ measure.
\\
That is $\mu_{\mathbb{P}}:=\int_{\mathcal{X}}k(x,\cdot)d\mathbb{P}(x)$.
\\
Kernel mean embedding serves as a unique representation of $\mathbb{P}$ in the RKHS $\mathcal{H}$. This holds provided  that $\mathcal{H}$ is characteristic. 
\begin{definition}
The RKHS $\mathcal{H}$ and the associated kernel k are said characteristic, when the mapping $\mu : \mathbb{P} \rightarrow \mathcal{H}$ is injective.
\end{definition}
%Hence, H is characteristic, if for any P,Q ∈ P, we have μP = μQ if and only if P = Q. 
When the mapping is injective, we have that $\mu_{\mathbb{P}}$ is uniquely associated with $\mathbb{P}$; thus, $\mu_{\mathbb{P}}$ is a unique representation of $\mathbb{P}$ in $\mathcal{H}$. 
%Characteristic kernels on X = Rd include {Gaussian, Matérn and Laplace}(Sriperumbudur et al., 2010).
%On the other hand, linear and polynomial kernels are not characteristic.
\\
Note that, by the reproducing property of RKHS $\langle f, k(x,\cdot) \rangle=f(x)$ we have:
\\
\begin{center}
    $E_{\mathbb{P}}[f(x)]=\langle f,\mu_{\mathbb{P}} \rangle_{\mathcal{H}}, \ \forall f \in \mathcal{H}$
\end{center}

>>>>

\section{Recovering Distributions from Gaussian RKHS Embeddings}
% \href{http://proceedings.mlr.press/v33/kanagawa14.pdf}
This paper covers the RKHS embedding approach to nonparametric statistical inference \cite{pmlr}.
The idea here is computing an estimate of the kernel mean in order to obtain an approximation of the underlying distribution of the observed random variable.
The kernel mean embedding $\mu_{\mathbb{P}}$ of a probability $\mathbb{P}$ corresponds to the feauture map $\phi(x)$ integrated with respect to the $\mathbb{P}$ measure.
\\
That is $\mu_{\mathbb{P}}:=\int_{\mathcal{X}}k(x,\cdot)d\mathbb{P}(x)$.
\\
Kernel mean embedding serves as a unique representation of $\mathbb{P}$ in the RKHS $\mathcal{H}$. This holds provided  that $\mathcal{H}$ is characteristic. 
\begin{definition}
The RKHS $\mathcal{H}$ and the associated kernel k are said characteristic, when the mapping $\mu : \mathbb{P} \rightarrow \mathcal{H}$ is injective.
\end{definition}
%Hence, H is characteristic, if for any P,Q ∈ P, we have μP = μQ if and only if P = Q. 
When the mapping is injective, we have that $\mu_{\mathbb{P}}$ is uniquely associated with $\mathbb{P}$; thus, $\mu_{\mathbb{P}}$ is a unique representation of $\mathbb{P}$ in $\mathcal{H}$. 
%Characteristic kernels on X = Rd include {Gaussian, Matérn and Laplace}(Sriperumbudur et al., 2010).
%On the other hand, linear and polynomial kernels are not characteristic.
\\
Note that, by the reproducing property of RKHS $\langle f, k(x,\cdot) \rangle=f(x)$ we have:
\\
\begin{center}
    $E_{\mathbb{P}}[f(x)]=\langle f,\mu_{\mathbb{P}} \rangle_{\mathcal{H}}, \ \forall f \in \mathcal{H}$
\end{center}
